%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.6, 21 May 2021) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%
%% Modded by Andrew Simonson (asimonson1125@gmail.com)
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and packages.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% Use (and optionally edit if necessary) this .tex if you
%% want to use an author-year reference style like APA(6)
%% for your publication list
\input{pubs-authoryear}

%% Use (and optionally edit if necessary) this .tex if you
%% want an originally numerical reference style like IEEE
%% for your publication list
% \input{pubs-num}

%% sample.bib contains your publications
\addbibresource{sample.bib}
\begin{document}
\name{Andrew Simonson}
\tagline{Seeking co-op or internship in Computer Science or Data Science for the summer and fall of 2023}
%% You can add multiple photos on the left or right
% \photoL{2.5cm}{Yacht_High,Suitcase_High}

\personalinfo{%
  % Not all of these are required!
  \email{asimonson1125@gmail.com}
  \phone{(240)-707-1486}
  \homepage{asimonson.com}
  \linkedin{simonsonandrew}
  \github{asimonson1125}
  %% You can add your own arbitrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
  %%
  %% For services and platforms like Mastodon where there isn't a
  %% straightforward relation between the user ID/nickname and the hyperlink,
  %% you can use \printinfo directly e.g.
  % \printinfo{\faMastodon}{@username@instace}[https://instance.url/@username]
  %% But if you absolutely want to create new dedicated info fields for
  %% such platforms, then use \NewInfoField* with a star:
  % \NewInfoField*{mastodon}{\faMastodon}
  %% then you can use \mastodon, with TWO arguments where the 2nd argument is
  %% the full hyperlink.
  % \mastodon{@username@instance}{https://instance.url/@username}
}

\makecvheader
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Projects}

\cvproject{AnalyzeRIT}{\githubProject{Imagine2023}}
Leader for the ongoing project with the Computer Science House to track the 2023 ImagineRIT festival via distributed system signal strength.\par\vspace{.15cm}
\cvtag{Python}
\cvtag{SciPy}
\cvtag{APIs}
\cvtag{SQL}


\divider

\cvproject{Slate}{\githubProject{Slate}|\hspace{.05in}\homepage{slate.csh.rit.edu}}
Event coordination web app that compiles participant calendar data and presenting statistics on the times with the best availability scores.  Service is live for Computer Science House members.\par\vspace{.15cm}
\cvtag{Python}
\cvtag{Flask}
\cvtag{LDAP}
\cvtag{SQL}
\cvtag{OAuth2}
\cvtag{JavaScript}


\divider


\cvproject{NationsGame Rolls Simulator}{\githubProject{NG-Rolls-Simulator}}
A NationsGame competition simulator for division predictions and statistical analysis, originally written in Python, ported to JavaScript for use in Discord bots.  Uses Discord.js and an undocumented NG-API to return processed player data to user.\par\vspace{.15cm}
\cvtag{Python}
\cvtag{JavaScript}
\cvtag{Node.js}
\cvtag{APIs}

\medskip

\cvsection{Activities}

\cvactivity{Computer Science House}{|}{\homepage{csh.rit.edu}}{Active Member}{May 2021 - Present}{Rochester Institute of Technology}
A living and learning community with an emphasis on hands-on learning and a strong social atmosphere. CSH helps its members grow as professionals with a focus on learning from each other through seminars and a yearly major project requirement.

\divider

\cvevent{FinTech}{Founding Member/Dev}{September 2021 - Present}{Rochester Institute of Technology}
A group derived from the RIT Financial Management Association dedicated to learning about financial management of equities using automated solutions developed by students.

\divider

\cvevent{BHS VEX Robotics}{President and Team Lead}{2015-2021}{Boonsboro High School}
An organization to design, build, and program robots to compete in the
annual VEX Robotics Competition at Boonsboro High School.
%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Skills}

\cvtag{Python}
\cvtag{JavaScript}
\cvtag{Java}
\cvtag{C++}
\cvtag{C}\par\vspace{.15cm}
\cvtag{HTML}
\cvtag{SQL}
\cvtag{MIPS Assembly}
\cvtag{LaTeX}\par\vspace{.15cm}

\divider\smallskip\vspace{.15cm}

\cvtag{Git}
\cvtag{Linux}
\cvtag{ArcGIS}
\cvtag{Angular}
\cvtag{Node}\par\vspace{.15cm}
\cvtag{React}
\cvtag{Flask}
\cvtag{Web Scraping}
\cvtag{OKD4}\par\vspace{.15cm}
\cvtag{Kubernetes}
\cvtag{PostgreSQL}
\cvtag{SQLAlchemy}

\medskip

\cvsection{Experience}

\cveventShort{Kitchen Staff}{\href{https://www.pretzelandpizzacreations.com/}{Pretzel and Pizza Creations}}{April 2021 -- August 2021}{Hagerstown, MD}
Worked part-time as a chef with a team to manage and fulfill orders and manage active ingredient supply.

\divider

\cveventShort{Election Official}{\href{https://www.washco-mdelections.org/}{Washington County Board of Elections}}{August 2020 -- December 2020}{Hagerstown, MD}
Trained in voter registry operations and provisional voting for the 2020 US Presidential Election.
\vspace{.15cm}

\cvsection{Education}

\cveventShort{Rochester Institute of Technology}{Computer Science B.S.}{Expected Graduation: May 2025}{Rochester, New York}
Third Year Standing\\
\textbf{GPA: 3.5}

\divider

\cveventShort{Boonsboro High School}{}{Sept 2016 -- June 2021}{Boonsboro, Maryland}
Graduated with highest honors\\
\textbf{GPA:} 4.2 (weighted out of 5)\\
\textbf{SAT:} 1500 (out of 1600)

\end{paracol}

\end{document}
